---
title: 'DataProducts: Week2'
author: "Nathan Day"
date: "1/28/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## My New Slide
Knit that shiz

***
A Slide without a title is formated with three asteriks

## Titles are two pounds
### A sub header is three
#### A sub sub header is four

## Lists require bullets
- Element 1
- Element 2

Or we could used numbers directly

1. Number One
2. Number Two

## Formatting Text

Plain text no asteriks

*italicized text with 1 asterik*

**Bold text with 2 asteriks**

Syntax: `for i in 1:10` use SO backticks

## R code
The same as mark down reports
```{r, comment = "", echo=TRUE}
head(mtcars)
```
## A plot slide
Same shit
```{r, fig.height=4, fig.width=4, fig.align='center', fig.cap = "fuck BC"}
library(ggplot2)
ggplot(mtcars, aes(mpg, hp, color = as.factor(cyl))) +
    geom_point() +
    stat_smooth()
```

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

